---
title: "Repeat extortion of Mexican businesses: Revision analysis"
author: "Patricio R. Estevez Soto"
email: "patricio.estevez.14@ucl.ac.uk"
date: "4/05/2016"
output:
  md_document:
    variant: "markdown"
pandoc_args: "--smart"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment="",
                      cache=TRUE,
                      dev=c("png", "CairoPDF"),
                      error=TRUE)
```

# Introduction

Script to analyze patterns of extortion victimization against Mexican businesses.

# Set up, data input and pre-process

## Session info

We first check details of the session and system, and for reproducibility, we set the random seed.

```{r session, cache=FALSE}
starttime <- proc.time()
date()
sessionInfo()
set.seed(42)
options(scipen=0)
```

## Load packages and functions

Next we load the packages that we will use.

```{r packages}
library(foreign)
library(ggplot2)
library(Cairo)
library(knitr)
library(texreg)
library(lme4)
library(glmmADMB)
library(classInt)
library(dplyr)
```


```{r import-data}
enve_all <- read.dbf("enve2014cuest_ciega_2014.dbf")
cat_entidades <- read.csv("cat_entidades.csv", head=TRUE)
area_level_tmp <- read.csv("state_level_data.csv", header=TRUE)
area_level <- merge(area_level_tmp, cat_entidades, by="CVE_ENT", all.x=TRUE)
scode <- read.csv("secode.csv", head=TRUE)
scode$Code <- scode$Code*10000
```


Quick overview of all the variables in the dataset

```{r overview-all}

summary(enve_all)

```

Now select only the relevant variables

```{r extortion-variable-selection}

enve_test <- data.frame(extortions=as.integer(as.character(enve_all$P26_10)))

enve_test$extortion_victim <- enve_all$P25_10
enve_test$extortions[enve_test$extortion_victim == 2] <- 0
summary(enve_test$extortions)
table(enve_test$extortions)

enve_test$extortion_victim
```

enve_test$CVE_UNICA <- as.integer(as.character(enve_all$ID_CONSECU))

enve_test$bribes <- as.integer(as.character(enve_all$P33))
summary(enve_test$bribes)

enve_test$bribes2 <- as.integer(as.character(enve_all$P33))

# 4 bribe cats
enve_test$bribe1 <- enve_all$P29_1
enve_test$bribe2 <- enve_all$P30_1
enve_test$bribe3 <- enve_all$P31_1
enve_test$bribe4 <- enve_all$P32_1

enve_test$bribes[with(enve_test,
                        bribe1 == 2 &
                        bribe2 == 2 &
                        bribe3 == 2 &
                        bribe4 == 2)] <- 0

summary(enve_test$bribes)

bribecols <- c("bribe1",
               "bribe2",
               "bribe3",
               "bribe4")

#bribe_col_test <- bribecols %in% names(enve_test)

colindbribe <- which(names(enve_test) %in% bribecols)

colindbribe

enve_test <- enve_test[,-colindbribe]

enve_test$CVE_ENT <- as.integer(as.character(enve_all$CVE_ENT))

enve_test$size <- enve_all$ID_ESTRATO
levels(enve_test$size) <- c("Large", "Medium", "Small", "Micro")

enve_test$sector <- enve_all$SECTOR_FIN

# subsector
enve_test$tempsub <- as.integer(as.character(enve_all$P1_1B))
enve_test$subsector <- cut(enve_test$tempsub, scode$Code, right=FALSE)
levels(enve_test$subsector) <- scode$Sector
enve_test$subsector <- droplevels(enve_test$subsector)
enve_test$subsector <- relevel(enve_test$subsector, ref="Retail")
levels(enve_test$subsector)


enve_test$hotrestbar <- enve_test$subsector
hotindx <- which(levels(enve_test$hotrestbar) == "HotelsRestBar")
levels(enve_test$hotrestbar)[-hotindx] <- 0
levels(enve_test$hotrestbar) <- c(0,1)

enve_test$years <- 2013 - as.numeric(as.character(enve_all$P3))
intyears <- classIntervals(enve_test$years, 5, style="quantile")
enve_test$yearsquant <- cut(enve_test$years, intyears$brks, right=TRUE,
                            include.lowest = TRUE)

enve_test <- merge(enve_test, homicidios, by="CVE_ENT", all.x=TRUE)

length(enve_test$extortions[is.na(enve_test$extortions)])
length(enve_test$bribes[is.na(enve_test$bribes)])

summary(enve_test)

summary(enve_test$bribes2)

enve_test$bribes2[is.na(enve_test$bribes2)] <- 0
summary(enve_test$bribes2)


colind <- which(names(enve_test)=="bribes")

enve_test2 <- enve_test[,-colind]

summary(enve_test2)


enve_test3 <- enve_test2

enve_test3$extortions[is.na(enve_test$extortions)] <- 0

summary(enve_test3)

```




