---
title: "Repeat extortion of Mexican businesses: Revision analysis"
author: "Patricio R. Estevez Soto"
email: "patricio.estevez.14@ucl.ac.uk"
date: "4/05/2016"
output:
  md_document:
    variant: "markdown"
pandoc_args: "--smart"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment="",
                      cache=TRUE,
                      dev=c("png", "CairoPDF"),
                      error=TRUE)
options(knitr.kable.NA = '--')
```

# Introduction

Script to analyze patterns of extortion victimization against Mexican businesses.

# Set up, data input and pre-process

## Session info

We first check details of the session and system, and for reproducibility, we set the random seed.

```{r session, cache=FALSE}
starttime <- proc.time()
date()
sessionInfo()
set.seed(42)
options(scipen=0)
```

## Load packages and functions

Install custom package, requires `devtools`.

```{r install-estevez}
devtools::install_github("prestevez/vicarp")
```

Next we load the packages that we will use.

```{r packages}
library(vicarp)
library(foreign)
library(ggplot2)
library(Cairo)
library(knitr)
#library(texreg)
library(lme4)
library(glmmADMB)
library(classInt)
library(dplyr)
library(reshape2)
```



## Data input

Load the data for the study.

```{r import-data}
enve_all <- read.dbf("enve2014cuest_ciega_2014.dbf")
cat_entidades <- read.csv("cat_entidades.csv", head=TRUE)
area_level_tmp <- read.csv("state_level_data.csv", header=TRUE)
area_level <- merge(area_level_tmp, cat_entidades, by="CVE_ENT", all.x=TRUE)
scode <- read.csv("secode.csv", head=TRUE)
scode$Code <- scode$Code*10000
```


Quick overview of all the variables in the dataset

```{r overview-all}

summary(enve_all)

```

Now select only the relevant variables

```{r extortion-variables-selection}

enve_test <- data.frame(extortions=as.integer(as.character(enve_all$P26_10)))

enve_test$extortion_victim <- enve_all$P25_10
enve_test$extortions[enve_test$extortion_victim == 2] <- 0

summary(enve_test$extortions)
table(enve_test$extortions)

enve_test$extortions_nas <- enve_test$extortions
enve_test$extortions[is.na(enve_test$extortions)] <- 0

summary(enve_test$extortions)
table(enve_test$extortions)

levels(enve_test$extortion_victim) <- c("yes", "no", "dk")
enve_test$extortion_victim <- relevel(enve_test$extortion_victim, ref = "no")

enve_test$rep_extortion_victim <- factor(enve_test$extortions)
levels(enve_test$rep_extortion_victim) <- c(0, 0,
                    rep(1, length(levels(enve_test$rep_extortion_victim)) - 2))

summary(enve_test$rep_extortion_victim)


summary(enve_test)
```



```{r bribes-variables-selection}

enve_test$bribes <- as.integer(as.character(enve_all$P33))
summary(enve_test$bribes)


# 4 bribe cats
enve_test$bribe1 <- enve_all$P29_1
enve_test$bribe2 <- enve_all$P30_1
enve_test$bribe3 <- enve_all$P31_1
enve_test$bribe4 <- enve_all$P32_1

enve_test$bribes[with(enve_test,
                        bribe1 == 2 &
                        bribe2 == 2 &
                        bribe3 == 2 &
                        bribe4 == 2)] <- 0

summary(enve_test$bribes)

enve_test$bribe_victim[enve_test$bribes > 0] <- 1
enve_test$bribe_victim[with(enve_test,
                        bribe1 == 2 &
                        bribe2 == 2 &
                        bribe3 == 2 &
                        bribe4 == 2)] <- 0

enve_test$bribe_victim[with(enve_test,
                        bribe1 == 9 &
                        bribe2 == 9 &
                        bribe3 == 9 &
                        bribe4 == 9)] <- 9

enve_test %>%
    mutate(bribe_victim = as.factor(bribe_victim)) -> enve_test

levels(enve_test$bribe_victim) <- c("no", "yes", "dk")

bribecols <- c("bribe1",
               "bribe2",
               "bribe3",
               "bribe4")

colindbribe <- which(names(enve_test) %in% bribecols)

enve_test <- enve_test[,-colindbribe]

enve_test$bribes_nas <- enve_test$bribes

enve_test$bribes[is.na(enve_test$bribes)] <- 0


summary(enve_test)
```

```{r other-variables-selection}
enve_test$CVE_UNICA <- as.integer(as.character(enve_all$ID_CONSECU))

enve_test$CVE_ENT <- as.integer(as.character(enve_all$CVE_ENT))

enve_test$size <- enve_all$ID_ESTRATO
levels(enve_test$size) <- c("Large", "Medium", "Small", "Micro")

enve_test$sector <- enve_all$SECTOR_FIN

# subsector
enve_test$tempsub <- as.integer(as.character(enve_all$P1_1B))
enve_test$subsector <- cut(enve_test$tempsub, scode$Code, right=FALSE)
levels(enve_test$subsector) <- scode$Sector
enve_test$subsector <- droplevels(enve_test$subsector)
enve_test$subsector <- relevel(enve_test$subsector, ref="Retail")
levels(enve_test$subsector)

### To exclude the subsectors with very few observations

# summary(enve_test)
# nrow(enve_test)
# enve_test %>%
#     filter(subsector != "Utilities") %>%
#     filter(subsector != "Corporate") -> enve_test_2
# 
# enve_test_2$subsector <- droplevels(enve_test_2$subsector)
# 
# levels(enve_test_2$subsector)
# nrow(enve_test_2)

enve_test$years <- 2013 - as.numeric(as.character(enve_all$P3))
intyears <- classIntervals(enve_test$years, 5, style="quantile")
enve_test$yearsquant <- cut(enve_test$years, intyears$brks, right=TRUE,
                            include.lowest = TRUE)

intyears_deciles <- classIntervals(enve_test$years, 10, style="quantile")
enve_test$years_deciles <- cut(enve_test$years, intyears_deciles$brks, right=TRUE,
                            include.lowest = TRUE)


enve_test <- merge(enve_test, area_level, by="CVE_ENT", all.x=TRUE)

length(enve_test$extortions[is.na(enve_test$extortions)])
length(enve_test$bribes[is.na(enve_test$bribes)])

## Summary of final dataset
summary(enve_test)

```
## Incident module

Add data from the incident module to briefly, **briefly**, analyse the distributions of extortion according to modus operandi.

``` {r incident-module}
enve_incidents_all <- read.dbf("enve2014delitos_ciega_2014.dbf")

# Selecting only those relevant for extortion (code 10)
enve_incidents_all$delito <- as.integer(as.character(enve_incidents_all$ID_DELITO))
enve_incidents <- enve_incidents_all[enve_incidents_all$delito == 10,]

incident_df <- data.frame(CVE_UNICA=as.integer(as.character(enve_incidents$ID_CONSECU)))

incident_df$delito <- enve_incidents$delito

incident_df$type <- as.character(enve_incidents$M5_1)
incident_df$type <- as.factor(incident_df$type)
levels(incident_df$type) <- c("Telephone", "Internet", "Street",
                                        "Premises", "Cobro de piso", "Other")

incident_df$simp <- incident_df$type
levels(incident_df$simp) <- c("Remote", "Remote", "In person",
                                        "In person", "In person", "Other")

# Transform the factors into dummy variables

type_dummy <- data.frame(model.matrix( ~ type -1 , data = incident_df))

simple_dummy <- data.frame(model.matrix( ~ simp -1 , data = incident_df))

incident_df <- cbind(incident_df, type_dummy, simple_dummy)

summary(incident_df)
```

Next we merge both incident-level and victim-level tables, and produce a new business-level table with counts based on the incident module.

```{r incident-victim-merge}

enve_incvic <- merge(incident_df, enve_test, by="CVE_UNICA", all.y = TRUE)

summary(enve_incvic)
nrow(enve_incvic)
nrow(enve_test)
length(unique(enve_incvic$CVE_UNICA))

enve_incvic %>%
    group_by(CVE_UNICA) %>%
    summarise(typeTelephone = sum(typeTelephone),
              typeInternet = sum(typeInternet),
              typeStreet = sum(typeStreet),
              typePremises = sum(typePremises),
              typeCobro.de.piso = sum(typeCobro.de.piso),
              typeOther = sum(typeOther),
              simpRemote = sum(simpRemote),
              simpIn.person = sum(simpIn.person),
              simpOther = sum(simpOther)) -> enve_type_counts

enve_type_counts[(is.na(enve_type_counts))] <- 0

nrow(enve_type_counts)

enve_type_counts %>%
    mutate(cap_count = simpRemote + simpIn.person + simpOther,
           propTel = typeTelephone/cap_count,
           propInternet = typeInternet/cap_count,
           propStreet = typeStreet/cap_count,
           propPremises = typePremises/cap_count,
           propPiso = typeCobro.de.piso/cap_count,
           propOther = typeOther/cap_count,
           propRemote = simpRemote/cap_count,
           propIn.person = simpIn.person/cap_count) -> enve_type_counts_and_props

enve_type_counts_and_props[is.na(enve_type_counts_and_props)] <- 0

enve_test %>%
    left_join(enve_type_counts_and_props, by = "CVE_UNICA") %>%
    mutate(estTel = round(propTel * extortions),
           estInternet = round(propInternet * extortions),
           estStreet =  round(propStreet * extortions),
           estPremises = round(propPremises * extortions),
           estPiso = round(propPiso * extortions),
           estOther = round(propOther * extortions),
           estRemote = round(propRemote * extortions),
           estIn.person = round(propIn.person * extortions)) -> enve_final

summary(enve_final)

```

# EDA

Re-do some of the EDA

## Univariate extortion analysis

Distribution, lorenz plots and poisson tests for the aggregated extortion counts in the screening questionnaire

```{r univariate-EDA}

extortion_columns1 <- c("extortions", "extortions_nas")

extortion_dist1 <- lapply(extortion_columns1, victim_table,
                          data = enve_final, print_option = "pandoc")

names(extortion_dist1) <- extortion_columns1

extortion_dist1

extortion_dist1 <- lapply(extortion_columns1, victim_table,
                          data = enve_final, print_option = "none")

names(extortion_dist1) <- extortion_columns1

ext1_vicum <- lapply(extortion_dist1, victim_cumulative)

lapply(ext1_vicum, kable, style = "pandoc", digits = 3)

```

```{r extortions1-lorenz}

lapply(extortion_columns1, victim_lorenz, 
       data = enve_final, family = "none")

victim_lorenz("extortions", enve_final, family = "poisson")

victim_lorenz("extortions", enve_final, family = "nbinom")

```

Now do some MC gini tests, Index of dispersion tests, and KS tests

```{r extortions1-tests}

mc_gini_test("extortions", enve_final, family = "poisson", plots = TRUE)
mc_gini_test("extortions", enve_final, family = "nbinom", plots = TRUE)

dispersion_batch("extortions", enve_final, print_option = "pandoc")

my_ks_test("extortions", enve_final)

my_ks_test("extortions", enve_final, family = "nbinom")

ext_chisq_poiss <- chisq_count("extortions", data = enve_final, B = 2000,
                               family = "poisson")

ext_chisq_poiss

ext_chisq_poiss_tb <- data.frame(ext_chisq_poiss$observed,
                                 Exp = ext_chisq_poiss$expected)[,c(1,2,4)]

kable(ext_chisq_poiss_tb, format = "pandoc", digits = 3, 
      caption = "Poisson expected counts")

ext_chisq_nbinom <- chisq_count("extortions", data = enve_final, B = 2000,
                               family = "nbinom")

ext_chisq_nbinom

ext_chisq_nbinom_tb <- data.frame(ext_chisq_nbinom$observed,
                                 Exp = ext_chisq_nbinom$expected)[,c(1,2,4)]

kable(ext_chisq_nbinom_tb, format = "pandoc", digits = 3, 
      caption = "Negative binomial expected counts")

```

## Univariate: other extortion types

Now do the univariate analysis for the rest of the extortion variables. First for the capped counts.

```{r extortions-capped-univariate-distribution}

extortion_columns_capped <- c("typeTelephone",
                              "typeInternet",
                              "typeStreet",
                              "typePremises",
                              "typeCobro.de.piso",
                              "typeOther",
                              "simpRemote",
                              "simpIn.person",
                              "cap_count")

extortion_dist_capped <- lapply(extortion_columns_capped, victim_table,
                          data = enve_final, print_option = "pandoc")

names(extortion_dist_capped) <- extortion_columns_capped
extortion_dist_capped


extortion_dist_capped_nformat <- lapply(extortion_columns_capped, victim_table,
                          data = enve_final, print_option = "none")

names(extortion_dist_capped_nformat) <- extortion_columns_capped

ext_capped_vicum <- lapply(extortion_dist_capped_nformat, victim_cumulative)

lapply(ext_capped_vicum, kable, style = "pandoc", digits = 3)


```

```{r extortion-capped-lorenz}

lapply(extortion_columns_capped, victim_lorenz, data = enve_final,
       family = "poisson")

lapply(extortion_columns_capped, victim_lorenz, data = enve_final,
       family = "nbinom")

```

Now do some hypothesis testing 

```{r capped-extortions-tests}

lapply(extortion_columns_capped, mc_gini_test, data = enve_final,
       family = "poisson", plots = TRUE) 

lapply(extortion_columns_capped, mc_gini_test, data = enve_final,
       family = "nbinom", plots = TRUE) 

dispersion_batch(extortion_columns_capped, enve_final, print_option = "pandoc")

ks_test_batch(extortion_columns_capped, enve_final, print_option = "pandoc", 
              family = "poisson")

ks_test_batch(extortion_columns_capped, enve_final, print_option = "pandoc", 
              family = "nbinom")

# poisson expected chisq

ext_cap_chisq_p <- lapply(extortion_columns_capped, function(x)
{
    tryCatch(chisq_count(x, data = enve_final, B = 2000), 
             error = function(e) NULL)
})

ext_cap_chisq_p

nullind <- which(unlist(lapply(ext_cap_chisq_p, is.null)))

ext_cap_chisq_p <- ext_cap_chisq_p[-nullind]

kable(chisq_tb(ext_cap_chisq_p), format = "pandoc", digits = 3)


ext_cap_p_tb <- lapply(ext_cap_chisq_p, function(x)
    {
    kable(data.frame(x$observed, Exp = x$expected)[,c(1,2,4)],
          format = "pandoc", digits = 3, caption = "Expected: Poisson")
    })


ext_cap_p_tb

# now for negbin

ext_cap_chisq_nb <- lapply(extortion_columns_capped, function(x)
{
    tryCatch(chisq_count(x, data = enve_final, B = 2000, family = "nbinom"), 
             error = function(e) NULL)
})

ext_cap_chisq_nb

nullind <- which(unlist(lapply(ext_cap_chisq_nb, is.null)))

ext_cap_chisq_nb <- ext_cap_chisq_nb[-nullind]

kable(chisq_tb(ext_cap_chisq_nb), format = "pandoc", digits = 3)


ext_cap_nb_tb <- lapply(ext_cap_chisq_nb, function(x)
    {
    kable(data.frame(x$observed, Exp = x$expected)[,c(1,2,4)],
          format = "pandoc", digits = 3, caption = "Expected: negbin")
    })


ext_cap_nb_tb





```



Now do the estimated counts

```{r estimated-extortion-univariate distributions}

extortion_columns_estimated <- c("estTel",
                              "estInternet",
                              "estStreet",
                              "estPremises",
                              "estPiso",
                              "estOther",
                              "estRemote",
                              "estIn.person")

extortion_dist_estimated <- lapply(extortion_columns_estimated, function(x) 
                                {
                                    if(mean(enve_final[,x]) == 0){message(paste0("skipping ", x, ". No obs."))}
                                    else{victim_table(x, data = enve_final, print_option = "pandoc")}
                                })

names(extortion_dist_estimated) <- extortion_columns_estimated

extortion_dist_estimated


extortion_dist_estimated_nfor <- lapply(extortion_columns_estimated, function(x) 
                                {
                                    if(mean(enve_final[,x]) == 0){message(paste0("skipping ", x, ". No obs."))}
                                    else{victim_table(x, data = enve_final, print_option = "none")}
                                })

names(extortion_dist_estimated_nfor) <- extortion_columns_estimated

ext_estim_vicum <- lapply(extortion_dist_estimated_nfor,
                          function(x) {if(is.null(x)){message("skipping NULL objects")}
                              else {victim_cumulative(x)}}
                          )

lapply(ext_estim_vicum, 
       function(x) {if(is.null(x)){message("skipping NULL objects")}
                    else {kable(x, style = "pandoc", digits = 3)}})

```

```{r extortion-estimated-lorenz}

lapply(extortion_columns_estimated, victim_lorenz, data = enve_final,
       family = "poisson")

lapply(extortion_columns_estimated, victim_lorenz, data = enve_final,
       family = "nbinom")

```


```{r estimated-extortions-tests}

lapply(extortion_columns_estimated, mc_gini_test, data = enve_final,
       family = "poisson", plots = TRUE) 

lapply(extortion_columns_estimated, mc_gini_test, data = enve_final,
       family = "nbinom", plots = TRUE) 

dispersion_batch(extortion_columns_estimated, enve_final, print_option = "pandoc")

ks_test_batch(extortion_columns_estimated, enve_final, print_option = "pandoc", 
              family = "poisson")

ks_test_batch(extortion_columns_estimated, enve_final, print_option = "pandoc", 
              family = "nbinom")

```

# Bivariate EDA

## Extortion prevalence

```{r ext-prevalence-vs-bribes}

ivs <- c("bribes",
         "bribe_victim",
         "size",
         "subsector",
         "yearsquant",
         "years_deciles")

ext_p_batch_chsq <- batch_chisq(df = enve_final, DV = "extortion_victim", IV = ivs)

kable(chisq_tb(ext_p_batch_chsq, stars = TRUE), "pandoc", 
      caption = "Chi-square tests between 'extortion prevalence' and a set of DV")

chisq_list(ext_p_batch_chsq, option = "observed", print_option = "pandoc")

chisq_list(ext_p_batch_chsq, option = "ratio", print_option = "pandoc")

chisq_list(ext_p_batch_chsq, option = "percent", print_option = "pandoc")


```

## Extortion distribution

```{r ext-distribution-vs-bribes}

ivs <- c("bribes",
         "bribe_victim",
         "size",
         "subsector",
         "yearsquant",
         "years_deciles")

ext_p_batch_chsq <- batch_chisq(df = enve_final, DV = "extortions", IV = ivs)

kable(chisq_tb(ext_p_batch_chsq, stars = TRUE), "pandoc", 
      caption = "Chi-square tests between 'extortion counts' and a set of DV")

chisq_list(ext_p_batch_chsq, option = "observed", print_option = "pandoc")

chisq_list(ext_p_batch_chsq, option = "ratio", print_option = "pandoc")

chisq_list(ext_p_batch_chsq, option = "percent", print_option = "pandoc")


```

## Extortion vs Years

First a brief EDA analysis of the years variable, using a facet plot of the bivariate relationship with extortion incidents.

```{r years-plots}

enve_test %>%
    select(extortions, years, yearsquant, years_deciles) -> gg_ext_years



years_scatterplots <- ggplot(gg_ext_years, aes(x = years, y = extortions))

years_scatterplots + geom_point() + theme_bw() + geom_smooth(method = "lm")

# Quintiles

years_scatterplots + 
    geom_point() + 
    theme_bw() + 
    facet_wrap(~ yearsquant, scales = "free_x") + 
    geom_smooth(method = "lm")

# For deciles

years_scatterplots + 
    geom_point() + 
    theme_bw() + 
    facet_wrap(~ years_deciles, scales = "free_x") + 
    geom_smooth(method = "lm")

```



To do tomorrow:
- Chi-square test function to test obs vs expected for counts
- Move on to state analysis as listed in notebook
- Move on to models
- Test
- Send

- calculate the true prevalence and incidence to make sure it matches the one I calculated for the state values
- If I do exclude the NAs, redo the EDA analysis
- Add chunk to load functions as needed.
- Then let's start adding the models, as including new state-level variables, would probably have to rerun all of them
- Also, will need to run ZIP and hurdle. should optimise the modelling strategy, as we know it can be extremely time consuming. (should probably exclude cols with NAs to avoid errors), will attempt all with glmmadmb.


